Extracting data for time slice analyses

### 2017-11-27 analyses/01-extract-data-for-analyses.Rmd
Tidy up code

```{r}
source("../functions/tree.age.fossil.R")

slug <- "Wright2017"

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

# Note from Wright 2017: MCC tree. Note that to properly timescale the tree [e.g., in R] you must first divide the branch lengths by the corresponding clock rate, (= 0.03517385), and then set the root.time to 485.4]

# Replace zero branches with minimu branch length
tree$edge.length[which(tree$edge.length == 0)] <- 
  min(tree$edge.length[-which(tree$edge.length == 0)])

# Multiply branches by 0.03517385
tree$edge.length <- tree$edge.length / 0.03517385

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

@@

## Loading the data
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))

tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

>>>>

```{r}
slug <- "Wright2017"

## Loading the data and tree
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

# Replace zero branches with minimum branch length
tree$edge.length[which(tree$edge.length == 0)] <- 
  min(tree$edge.length[-which(tree$edge.length == 0)])

# Note from Wright 2017: MCC tree. Note that to properly timescale the tree [e.g., in R] you must first divide the branch lengths by the corresponding clock rate, (= 0.03517385), and then set the root.time to 485.4]
# Divide branches by 0.03517385
tree$edge.length <- tree$edge.length / 0.03517385

@@

## Loading the data and tree
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
tree <- read.nexus(paste0("../data/trees/", slug, ".nex"))

# Replace zero branches with minimum branch length
tree$edge.length[which(tree$edge.length == 0)] <- 
  min(tree$edge.length[-which(tree$edge.length == 0)])

@@

## Loading the data and tree
matrix <- ReadMorphNexus(paste0("../data/matrices/", slug, ".nex"))
tree <- read.nexus(paste0("../data/trees/", slug, ".tre"))

# Replace zero branches with minimum branch length
tree$edge.length[which(tree$edge.length == 0)] <- 
  min(tree$edge.length[-which(tree$edge.length == 0)])
